Dynamical Properties of Molecular Gas Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-07 WRITEUP/ms.tex
write some more

\author{T. K. Daisy Leung\altaffilmark{1, 2}}
\author{Andrea Pallottini \altaffilmark{3, 4}}
\author{Andrea Ferrara \altaffilmark{4, 5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7}}

\altaffiltext{1}{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, Simons Foundation, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli IPMU, The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
\email{tleung@astro.cornell.edu}

\begin{abstract}
We present results from the first study investigating the dynamical properties of molecular clouds
and their evolution in galaxies at Epoch of Reionization using state-of-the-art cosmological
zoom-in simulation, which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback via
kinetic and thermal energies. We find that ..
\end{abstract}
%\keywords{infrared: galaxies --
%          galaxies: high-redshift --
%          galaxies: ISM --
%          galaxies: evolution --
%          galaxies: starburst --
%          radio lines: ISM}

@@

At high redshifts, galaxies have higher star formation rates (SFR) and smaller sizes {\bf cite needed?}, thus are expected to have more \ion{H}{2} regions and ionized gas, and more intense radiation stellar feedbacks. Since also the metallicity and dust content should be lower {\bf cite?}, this affects the shielding of UV photons, heating and cooling mechanisms. Such differences in turn can have a role in regulating the thermal and chemical structures of their ISM, and thus, their multi-phase ISM differ from nearby galaxies.
%
Since \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies since the cosmic dark ages.

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, the ISM properties of \highz galaxies
have only been studied observationally in a handful of (strongly-lensed)
galaxies, using spatially resolved tracers such as
dust continuum, and CO and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that the ISM of $z$\ssim2 galaxies are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
\AP{i think the passage to "why we focus on eor galaxies" should be detailed a bit more}
However, it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6
that dominates  \SF at the epoch of reionization which is responsible for producing the
ionizing photons that reionized the universe.

@@

% radiative feedback --> NT pressure
Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernova, OB/AGB stars to account for energy dissipations. To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell when supernovae explode. The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy, and radiation pressure (on the dust and gas) is also included \citep[see][for details]{Pallottini17a}.

Details on the properties of \flower, the main galaxy in our simulation, are discussed in \citet{Pallottini17b}.
%
Briefly, by \z$\sim$6, \flower is a LBG hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc. At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne. It is therefore a prototypical galaxy at \z$\sim$6.

\subsection{Star Formation History} \label{sec:sfh}

\AP{i moved the section here, as I see it as part of motivation for the workflow; however, at the moment I do not see the stellar mass maps as figure that are needed; if they stay i would label their evolutionary stage in the SFR history plot.}

One of the advantage of studying the dynamical properties of molecular structures at
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
as a function of time.
This is advantageous especially at early cosmic epochs,
when the densest structures are beginning to form;
gas is constantly being accreted onto the central galaxy from the cosmic web and
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding
galaxies can disrupt the main disk and arms, likely leading to different dynamical states
for the molecular structures (e.g., some may disperse while others may agglomerate into more massive
structures). % mainly expecting differences in alpha_vir, sigma, M_cl.

We show the \SF history of \flower in \Fig{SFH}, where
the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
The SFR plotted in Figure 2 of \citet{Pallottini17b}
is a factor of two higher than shown here since they also include contributions from
massive satellites galaxies within the surrounding $\approx$50\,kpc, which
are accreted onto \flower at \z$\lesssim$\,2.}
as it evolves from an actively accreting phase to
a starburst phase after a major merger and then back to a relatively quiescent phase
over the few hundred Myr simulated in our simulation.
The SFR of \flower is calculated based on existing young stellar population, which is
defined to have an age of $t_{\rm age}<$\,10\,Myr.

Given the stochasticity in the \SF history of \flower,
we show the scaling relations found for two particular snapshots \AP{in the text I would refer to snapshots as to evolutionary stages of the galaxy (and make the link between the two in the method section)} as examples in \Sec{singless},
since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
most extreme variations in the cloud dynamics) --- one of which \flower is
actively accreting materials from its surrounding (top panel of \Fig{phases})
and another of which \flower is undergoing
a starburst phase after a major merger (bottom panel of \Fig{phases}).

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}
\caption{
	Star formation history of \flower \AP{if possible I would combine it with Fig. \ref{fig:phases} (as in the talk), or remove
	Fig. \ref{fig:phases}, as at the moment it does not add much to the discussion.
	}.
% f_gas history?
\label{fig:SFH}}
\end{figure*}

\begin{figure}[htbp]
\centering
\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}
\\ [-5em]
\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}
\caption{
Projected stellar mass distribution of \flower during one of its accretion phases
at an early stage of its evolution (top) and during one of its major starburst phases
after a major merger (bottom).
\label{fig:phases}}
\end{figure}

\subsection{Structure identification} \label{sec:method}

To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a} but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the cells in the simulation into non-overlapping tiles, which are stored in a k-dimentional tree (aka k-d tree). It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across the tiles. In the customized version used for this study, \AP{the following is true but I do not think we should write it in this way ...} \DL{right, will change when we submit paper, just being sarcastic here.} we modified \ncode{yt} in order for it to actually work.

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).

\AP{maybe we can refer to the PPP vs PPV method discussion in Mordecai's paper}
We note that this process is in essence similar to
identifying molecular structures based on the noise levels of surface density maps
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying
``clumps'' based on/after applying $\sigma$-clipping,
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind},
and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single snapshot.
\label{fig:h2density}}
\end{figure}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.32}.png}
  \\[-5.5em]
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.53}.png}
\caption{
MC identified by applying
volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
	Color shows the projected H$_2$ surface density. {\bf this should be H2 density 1/cm$^{-2}$?!} \AP{if i recall correctly, this is not the projected h2 density, but the mass averaged h2 density field. in any case, we should compress the information, by having a less figures showing multplie cuts (e.g. 3 of them by using thinner lines should suffice in conveining the overview properly); additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}
% yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
\label{fig:MC}}
\addtocounter{figure}{-1}
\end{figure*}

@@

In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range where ``clumps/structures'' are 
found based on the Minkovsky analysis presented by \citet{Pallottini17b}.
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of \AP{I would directly use labels in logspace} $n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no significant differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we impose an addition constraint such that an identified structure only survives if it spans at least 10 cells in 3D position-position-position (PPP) space. We caution that one caveats of such constraint is that we can only examine the parameter space of ``cloud'' scaling relations at ``cloud'' size $R\gtrsim100$\,pc.

@@

\subsection{Cloud Scaling Relations}
\AP{I see 2 main possible approaches to the presentation of the results
%
(a) focus on a single snapshot, analyze the cloud scaling relation by varing the cuts and then by varing the snapshot; after that one can discuss the stability (toomre analysis) of the clumps (that should help in discussing the origin) and the CMF (more speculative, because of the resolution issues).
%
(b) discuss each scaling relation one at a time; probabily in this case an introductionary subsection is needed to explain that different cuts yields no qualitative differences; toomre and CMF as before.
%
Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s).
%
I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g. the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
%
Of course alternative approaches are possible, but right now these two seem to be the more natural ones.
}

Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$),
the ``cloud'' mass ($M_{\rm cl}$),
the ``cloud'' size ($R$),
the Mach number ($\mathcal{M}$),
the velocity dispersion ($\sigma$), and the
gas surface density ($\Sigma_{\rm gas}$)
to describe/characterize their dynamics.
We show in \Fig{} the MC distributions in terms of their
molecular gas mass, radius, gas mass fraction ($f_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ +
$M_*$)).
% plt.hist($M_{\rm cl}$), color by two different mass range.. ~2E7?
% plt.hist($R_{\rm cl}$), using same color scheme
% for f_gas, same color scheme
We note that the distributions vary for different snapshots, depending on
the gas surface density, the morphology, and the evolutionary stage of \flower.
The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
the order of 10$^{6.5}$\,\Msun for the densest MC identified.
Gas mass fractions of the MCs vary between $f_{\rm gas}\approx$xxx$-$0.xx.
% which may determine the ``cloud'' mass if these MCs are formed due to gravitational
% instabilities. We show gas fraction as a function of ``cloud'' mass in \Fig{}.
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

We find that the local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities.
\AP{i would put the following as a footnote or this point might be moved; alternatively these points (see also the emails) can be treated when dealing with the stability analysis}
We find comparable velocity dispersion derived by taking the root mean square ($\sigma^{\rm rms}$) versus
that derived using thermal and non-thermal pressure \AP{i would not introduce additional symbols if they are not used elsewhere} ($\sigma^{P+P_{\rm nt}}$), indicating that
rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion (i.e., $\sigma$\eq$\sigma^{\rm rms}$).
In \Sec{Q}, we also measure the contributions to the extracted velocity dispersions of the
MCs due to galactic rotation and shear.

>>>>

\author{T. K. Daisy Leung\altaffilmark{1, 2}}
\author{Andrea Pallottini\altaffilmark{3, 4}}
\author{Andrea Ferrara\altaffilmark{4, 5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7, 8}}

\altaffiltext{1}{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, Simons Foundation, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (IPMU), The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
\altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}
\email{tleung@astro.cornell.edu}

\begin{abstract}
We study the dynamical properties of molecular clouds and their temporal evolution in a prototypical galaxy 
at the Epoch of Reionization using state-of-the-art cosmological zoom-in simulation, 
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback via
kinetic and thermal energies. 
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify molecular complexes (MC) and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
We find that the MC of \flower are highly supersonic, with large velocity dispersion ($\sigma\approx$\,200\,\kms) comparable to 
those observed in gas-rich galaxies in the local universe as well as at the peak epoch of cosmic \SF. 
The mass scale of the MCs is of the order $10^{6.5-8}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
corresponds to the arms of the main disk of \flower and breaks down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
We find that the ...
The MCs in the satellites..
consistent with PVE.
We find no temporal variations in the MC physical properties over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. Higher resolution cosmological zoom-in simulations 
will shed light into ... , as we .... from observations.
\end{abstract}
%\keywords{infrared: galaxies --
%          galaxies: high-redshift --
%          galaxies: ISM --
%          galaxies: evolution --
%          galaxies: starburst --
%          radio lines: ISM}

@@

Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies 
since the cosmic dark ages.
Current consensus is that at higher redshifts, galaxies have higher 
star formation rates (SFR) \citep{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and 
smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to galaxies found in the local Universe, 
and thus, they are expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks. 
Since their metallicity and dust content are also expected to be lower as they are assembling, 
this affects the shielding of UV photons, heating and cooling mechanisms in this early systems. Such differences in turn can have a role in regulating the thermal and chemical structures of their ISM, and thus, their multi-phase ISM differ from nearby galaxies.
%
% talk about dynamical states of MCs of different galaxies? Even in the local universe, where the most detailed \obs can be done, we see variations in cloud properties in different galaxy populations (see e.g., Hughes10a, MNRAS, 406, 2065; Hughes+13b, ApJ, 779, 46), maybe also Meidt+13, apj, 779,45?. Thus, obvious to pose the question what are the dynamical states of the MCs of the first galaxies and how do they differ from nearby universe, and analogous to any of the nearby \galpop?
%

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, the ISM properties of \highz galaxies
have only been studied observationally in a handful of (strongly-lensed)
galaxies, using spatially resolved tracers such as
dust continuum, and CO and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that the ISM of $z$\ssim2 galaxies are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
On the other hand, the main source of reionization --- the first stars and first galaxies --- 
are ......
it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6
that dominates  \SF at the epoch of reionization which is responsible for producing the
ionizing photons that reionized the universe.

@@

% radiative feedback --> NT pressure
Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae and OB/AGB stars to account for energy dissipations. To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell when supernovae explode. The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy. Radiation pressure on the dust and gas is also included (see \citealt{Pallottini17a} for details).

Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}.
Briefly, by \z$\sim$6, \flower is a LBG hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc. At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne. It is therefore a prototypical galaxy at \z$\sim$6.

The simulation data contain information such as the density ($\rho$) and velocity ($v_x$, $v_y$, and $v_z$) fields, from which we calculate 
the physical properties of each MC, such as mass and velocity dispersion.
Due to the nature of our AMR simulation, we regrid the simulation data into uniform grids for the analysis presented in this paper. 
The grid size is defined 
based on the highest resolution of the simulation data (i.e., the less refined regions are supersampled in the resulting uniform grids).

\subsection{Star Formation History} \label{sec:sfh}
One of the advantage of studying the dynamical properties of molecular structures at
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
as a function of time.
This is advantageous especially at early cosmic epochs,
when the densest structures are beginning to form;
gas is constantly being accreted onto the central galaxy from the cosmic web and
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding
galaxies can disrupt the main disk and arms, likely leading to different dynamical states
for the molecular structures compared to more evolved galaxies found at 
a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive
ones). % mainly expecting differences in alpha_vir, sigma, M_cl.

We show the \SF history of \flower in \Fig{SFH}, where
the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
The SFR plotted in Figure 2 of \citet{Pallottini17b}
is a factor of two higher than shown here since they also include contributions from
massive satellites galaxies within the surrounding $\approx$50\,kpc, which
are accreted onto \flower at \z$\lesssim$\,2.}
as it evolves from an actively accreting phase to
a starburst phase after a major merger, and then back to a relatively quiescent phase
over the few hundred Myr simulated in our simulation.
The SFR of \flower is calculated based on existing young stellar population, which is
defined to have an age of $t_{\rm age}<$\,10\,Myr.

Given the stochasticity in the \SF history of \flower,
we show the scaling relations found for two particular snapshots/evolutionary stages of \flower
as examples in \Sec{singless} to illustrate the salient points of the discussion,
since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
most extreme variations in the cloud dynamics) --- one of which \flower is
actively accreting materials from its surrounding (top panel of \Fig{SFH})
and another of which \flower is undergoing
a starburst phase after a major merger (bottom panel of \Fig{SFH}).

\begin{figure*}[htbp]
\centering
\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/daisyleung2.pdf}
\caption{
	Top right: Star formation history of \flower.
	Projected stellar mass distribution of \flower during one of its accretion phases
	at its early stage of evolution {\it (a)}; during one of its major starburst phases
	after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
% f_gas history?
\label{fig:SFH}}
\end{figure*}

\subsection{Structure identification} \label{sec:method}
To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (aka k-d tree). It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across the tiles. 
In the customized version used for this study, we modify the function to enhance the stability of the code (which essentially means we fixed the bugs in order for it to actually work).

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
We note that this process is in essence similar to
identifying molecular structures based on the noise levels of surface density maps
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying
``clumps'' based on/after applying $\sigma$-clipping,
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind},
and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).
We note that, owing to the nature of \obs, such structures are identified 
in position-position-velocity (PPV) space in observational studies, whereas in simulations, one has the 
full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
Existing studies find a good correspondence in the dynamical properties extracted in
PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, 
Pan15a, Ibanez-Mejia16a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations). 
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single snapshot, corresponding to the 
accreting phase shown in \Fig{SFH}.
\label{fig:h2density}}
\end{figure}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.32}.png}
  \\[-5.5em]
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.53}.png}
\caption{
MC identified by applying
volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
	Color shows the projected H$_2$ surface density. {\bf this should be H2 density 1/cm$^{-2}$?!} \AP{if i recall correctly, this is not the projected h2 density, but the mass averaged h2 density field. in any case, we should compress the information, by having a less figures showing multplie cuts (e.g. 3 of them by using thinner lines should suffice in conveying the overview properly); additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}
% yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
\label{fig:MC}}
\addtocounter{figure}{-1}
\end{figure*}

@@

In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see analysis presented by \citealt{Pallottini17b}).
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we impose an addition constraint such that an identified structure only survives if it spans at least 10 cells in PPP space. We caution that one caveats of such constraint is that we can only examine the parameter space of ``cloud'' scaling relations at ``cloud'' size $R\gtrsim100$\,pc.

@@

\subsection{Cloud Scaling Relations}

\AP{I see 2 main possible approaches to the presentation of the results
%
(a) focus on a single snapshot, analyze the cloud scaling relation by varying the cuts and then by varying the snapshot; after that one can discuss the stability/toomre analysis of the clumps (help in discussing the origin) and the CMF.
%
(b) discuss each scaling relation one at a time; probabily an introductionary subsection is needed to explain that different cuts yields no qualitative differences.
%
Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s).
%
I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g. the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
}
\DL{agreed, but will move things around later, after the report and after most of the content is ready.}

Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$),
the ``cloud'' mass ($M_{\rm cl}$),
the ``cloud'' size ($R$),
the Mach number ($\mathcal{M}$),
the velocity dispersion ($\sigma$), and the
gas surface density ($\Sigma_{\rm gas}$)
to describe/characterize their dynamics.

The mass of an MC is calculated from the uniformly-gridded 3D density field,
integrating over all zones of the MC, multiplied by its volume. 
The size of an MC ($R$) is defined assuming spherical geometry (i.e., 
the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
the one-dimensional non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{xyz} \sum_{i}^N \rho_i \left(\mathbf{v} - \mathbf{\bar v}\right)_{xyz}^2}{\sum_i^N \rho_i},
\end{equation}
where $N$ is the number of zones of each MC.
The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities.
\AP{i would put the following as a footnote or this point might be moved; alternatively these points (see also the emails) can be treated when dealing with the stability analysis}
We find comparable velocity dispersion derived by taking the root mean square versus
that derived using thermal and non-thermal pressure, indicating that
rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
We quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion ($\sigma$).

We show in \Fig{dist} the MC distributions in terms of their
molecular gas masses, radii, gas mass fraction ($sf_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ +
$M_*$)).
We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
the order of 10$^{6.5}$\,\Msun for the densest MC identified.
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).
